A Topography of Climate Change Research

### 2018-07-23 pres/CC_Topography_EASST_Callaghan.tex
EASST pres

\usepackage[LGR,T1]{fontenc}
\usepackage[utf8]{inputenc} 
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{booktabs}
\usepackage{framed}

@@

\definecolor{rd}{HTML}{2F2A40}
\definecolor{methods}{HTML}{C6C6C6}
\definecolor{research}{HTML}{8F84BE}
\definecolor{skills}{HTML}{7A7A7A}
\definecolor{rc}{HTML}{AC152A}

\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}

@@

\begin{frame}{Introduction}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\begin{figure}
			\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
			\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item<2-> Topography is a description of a landscape
				\item<3-> Topics (from the Greek \textgreek{τόπος}, place) can describe the features of body of text
			\end{itemize}
		\end{center}
	\end{column}
	\end{columns}
\end{frame}

@@

\begin{frame}{Motivation}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{figure}
		\includegraphics<1>[width=1\linewidth]{../plots/volume_variety_AR0}
		\includegraphics<2>[width=1\linewidth]{../plots/volume_variety_AR1}
		\includegraphics<3>[width=1\linewidth]{../plots/volume_variety_bible_AR1}
		\includegraphics<4>[width=1\linewidth]{../plots/volume_variety_bible_AR2}
		\includegraphics<5>[width=1\linewidth]{../plots/volume_variety_bible_AR3}
		\includegraphics<6>[width=1\linewidth]{../plots/volume_variety_bible_AR4}
		\includegraphics<7>[width=1\linewidth]{../plots/volume_variety_bible_AR5}
		\includegraphics<8->[width=1\linewidth]{../plots/volume_variety_bible_AR6}
		\end{figure}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\only<1>{\framebox[1.1\width]{A matrix of documents x words } \par}
		\only<2>{\framebox[1.1\width]{AR1: 1,848 documents x 3,528 words } \par}
		\only<3>{\begin{framed}
			The Luther Bible: 1,189 documents (chapters) x 11,973 words
			\end{framed}}
		%\only<3>{\framebox[1.1\width]{The Luther Bible: \par 1,189 documents (chapters) x 11,973 words } \par}
		\only<4>{\framebox[1.1\width]{AR2: 6,941 documents x 15,781 words } \par}
		\only<5>{\framebox[1.1\width]{AR3: 18,728 documents x 27,730 words } \par}
		\only<6>{\framebox[1.1\width]{AR4: 44,000 documents x 45,388 words } \par}
		\only<7>{\framebox[1.1\width]{AR5: 108,277 documents x 75,553 words } \par}
		\only<8->{\framebox[1.1\width]{AR6: 128,357 documents x 86,149 words } \par}
		\end{center}
		\only<9->{		
		\begin{center}
			\begin{itemize}
				\item Comprehensive, credible and relevant assessments become
				more challenging as the literature grows
			\end{itemize}
		\begin{remark}[]
			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
		\end{remark}
		\end{center}
	}
	\end{column}
\end{columns}

@@

\only<3->{
\textbf{Steps}
\begin{enumerate}
	\item Download documents from Web of Science (WoS)
	\item Match documents to reference lists from IPCC reports
	\item Topic model stemmed document abstracts
\end{enumerate}
}
\end{frame}

@@

		\normalsize
		\begin{itemize}
			\item \citep{Haunschild2016}
			\item 309,697 documents
		\end{itemize}
	\end{column}
	\begin{column}{0.35\linewidth}
		\textbf{Caveats}
		\begin{itemize}
			\item Not perfect query
			\item WoS not all peer-reviewed literature
			\item Missing grey literature
			\item Missing relevant literature not directly about climate change
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

@@

	For each Reference:
	\begin{itemize}
		\item Check for case-insensitive title matches
		\item Calculate the Jaccard similarity score for two word every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
	\end{itemize}
\end{frame}

@@

@@

%\begin{frame}{Preliminary results - explanation}
%
%\begin{columns}
%	\begin{column}{0.5\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/biomass_eg.png}
%		\end{center}
%	\end{column}
%	\begin{column}{0.5\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Documents are mixtures of topics, based on the words which occur in them
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - Map}
%
%\begin{figure}
%			\includegraphics[width=\linewidth]{../plots/pca_map.png}
%			\caption{Topic Map, with topics placed according to Principal Component Analysis of topic-term matrix}
%\end{figure}
%
%\end{frame}

\begin{frame}{Results - structure}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}	
			\vspace*{-0.1\linewidth}
			\includegraphics[width=\linewidth]{../plots/network_wg_654}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
	%	\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
		\begin{center}
			\begin{itemize}
				\item<1-> Topics describe comprehensible themes in climate change research
				\item<2-> Matching topics to the IPCC working group from which the majority of the topics are referenced in, a structure is generated based on topic-document correlations
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}

	\begin{table}

		\input{../tables/654_wg_1_2}

	\end{table}

\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}

\begin{table}

	\input{../tables/654_wg_1_3}

\end{table}

%%%%%%%

\begin{frame}{Results - Inter-working Group topics - WG 2 and 3}

\begin{table}

\input{../tables/654_wg_2_3}

\end{table}

%%%%%%%%
%% RESULTS - DEVELOPMENT
%\begin{frame}{Results - Development}
%\only<1->{
%\begin{figure}
%	\includegraphics[width=0.8\linewidth]{../plots/development/662_sus}	
%\end{figure}
%}
%\only<1->{
%	\centering
%	\textbf{Message}
%}
%\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{../plots/development/662_holocene}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Basic climate science topics are not as prominent as they were previously}
}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{../plots/development/662_sus}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Sustainable development, and research agendas are more prominent}
}
\end{frame}

\begin{frame}
	The documents that underpin this growth
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.6\linewidth]{../plots/development/ar5_growth}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Fast growing topics in AR5 were on urban systems, negative emissions, buildings, consumption, biodiversity and risks}
}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
\begin{figure}
	\includegraphics[width=0.8\linewidth]{../plots/development/ar6_growth}	
\end{figure}
}
\only<1->{
	\centering
	\textbf{Negative emissions topics continue to grow,}
}
\end{frame}

%%%%%%%%%

%\begin{frame}{Preliminary results - structure - WGI}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
%		\begin{center}
%			\begin{itemize}
%				\item The largest topic in WGI is on models.
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - WGII}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item The largest primarily WGII topic is on climate change impacts
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - WGIII}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item The largest WGIII topic is on emissions reductions.
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - other clusters}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\hspace*{-0.1\linewidth}
%			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - structure - Sustainability}
%
%
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}			
%			\includegraphics[width=\linewidth]{../plots/sustainability}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - Sustainability}
%
%
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}			
%			\includegraphics[width=\linewidth]{../plots/health_sustain_386}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item The flatness of its distribution across documents indicates a topic that occurs
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%%% Sus table
%
%\begin{frame}{Preliminary results - structure - Sustainability}
%\begin{table}
%	\footnotesize
%	\renewcommand{\arraystretch}{2}
%\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
%	\toprule 
%	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
%	\midrule 
%	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\ 
%	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\ 
%	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\ 
%	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\ 
%	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
%	\bottomrule
%\end{tabular} 
%
%\end{table}
%
%\end{frame}

%\begin{frame}{Preliminary results - growth}
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/top_20_386}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Negative emissions related topics have shown strong growth since the end of AR5
%				\item As have topics on cities and extreme weather events
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - growth - biochar}
%
%
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}
%
%		\medskip
%
%			\begin{itemize}
%				\item Biochar has emerged as an entirely new topic in the last 10 years
%			\end{itemize}
%		\end{center}
%
%\end{frame}

%\begin{frame}{Preliminary results - gaps in coverage}
%
%How can we get a sense of which topics are better covered in IPCC reports?
%
%\begin{itemize}
%	\item Each document \(d\) either matches or does not match an IPCC reference
%	\item For each topic \(h\), we can sum the scores for each category of document
%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
%\end{itemize}
%
%\end{frame}

\begin{frame}{Results - topic representation in IPCC reports}

How can we get a sense of which topics are better covered in IPCC reports?

We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus

%\begin{itemize}
%	\item Each document \(d\) either matches or does not match an IPCC reference
%	\item For each topic \(h\), we can sum the scores for each category of document
%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
%\end{itemize}

\begin{frame}{Results - topic representation in IPCC reports}

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_662_all.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils and plants are less well represented
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Results - topic representation in IPCC reports}

	\begin{figure}
			\includegraphics[width=0.8\linewidth]{../plots/ipcc_representation/ipcc_rep_662_ARs}
	\end{figure}

\begin{frame}{Results - topic representation in IPCC reports}

	\includegraphics[width=0.8\linewidth]{../plots/ipcc_coverage_by_wg_654.png}

\begin{frame}{Results - AR6 outlook}

Outlines for the sixth assessment report have already been published.

The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a [simplified] topic score for each chapter.

These scores were summed and were compared to the corpus in general in the same way as with past reports

\begin{frame}{Results - topic representation in IPCC reports}

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_662_AR6.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils and plants are less well represented
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

%\begin{frame}{Next steps}
%	\begin{itemize}
%		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
%		\item Further analysis of new model
%		\item (Manual) comparison of (AR6) topics with AR6 outline
%	\end{itemize}
%\end{frame}

%\begin{frame}{Conclusions}
%
%
%\begin{itemize}
%	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
%	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
%	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
%	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
%	\item By uncovering the structure at scale of a large collection of documents, and by enabling the discovery of documents relevant to specific topics or combinations of topics, this approach can provide for more comprehensive and salient scientific assessments.
%\end{itemize}
%
%\end{frame}

%\begin{frame}{Extra results - Journals}
%
%\begin{columns}
%	\begin{column}{0.55\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/journals/journal_papers.png}
%		\end{center}
%	\end{column}
%	\begin{column}{0.45\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Nature has been publishing about climate change for a long time
%				\item Plos One has very recently overtaken all other journals
%				\item The number of journals has risen very steeply
%			\end{itemize}
%		\includegraphics[width=0.9\linewidth]{../plots/journals/n_journals.png}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Extra results - Journals}

%\begin{columns}
%	\begin{column}{0.55\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/journals/journal_entropy_386.png}
%		\end{center}
%	\end{column}
%	\begin{column}{0.45\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Journal Entropy describes the distribution of topics in a journal \citep{Hall2008a}
%				\item High values mean the journal deals with a wider range of topics
%			\end{itemize}
%			\[  H(z\rvert c,y) = -\sum_{i=1}^{K} \hat{p}(z_i \rvert c,y) \; log \; \hat{p}(z_i \rvert c, y) \]
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Extra results - Journals}
%
%	\includegraphics[width=\linewidth]{../plots/journals/journal_topics_386.png}
%
%\end{frame}

%\begin{frame}{Outlook}
%
%\begin{figure}
%
%\tiny
%
%\begin{ganttchart}[
%	y unit title=0.3cm,
%	y unit chart=0.5cm,
%	x unit= 0.2cm,
%	vgrid,hgrid,
%	vgrid={{dotted,dotted,black}},
%	title height=1,
%	%     title/.style={fill=none},
%	title label font=\bfseries\scriptsize,
%	%bar/.style={fill=blue},
%	bar height=0.7,
%	bar label font=\tiny,
%	%   progress label text={},
%	group right shift=0,
%	group top shift=0.7,
%	group height=.3,
%	group peaks width={0.2},
%	inline]{1}{42}
%	\gantttitle{2017}{9}
%	\gantttitle{2018}{12}
%	\gantttitle{2019}{12}
%	\gantttitle{2020}{9} \\
%	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
%	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
%	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
%	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
%	
%	% HERTIE
%	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
%	
%	% HERTIE
%	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
%	
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
%	
%	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
%	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
%	
%	
%	
%\end{ganttchart} 
%
%\end{figure}
%
%\end{frame}

\begin{frame}{Frame Title}
	\small
	\bibliography{../Mendeley.bib}
\end{frame}

>>>>

%\usepackage[LGR,T1]{fontenc}
%\usepackage[Latin, Greek]{ucharclasses}
\usepackage[utf8]{inputenc} 
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{polyglossia}
\usepackage{textgreek}
\usepackage{appendixnumberbeamer}

@@

\newcommand{\backupbegin}{
	\newcounter{finalframe}
	\setcounter{finalframe}{\value{framenumber}}
}
\newcommand{\backupend}{
	\setcounter{framenumber}{\value{finalframe}}
}

%\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}

@@

\begin{frame}{Introduction}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\begin{figure}
				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
				\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item<2-> Topography is a description of a landscape
				\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of body of text
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{Motivation - Big Literature}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{figure}
			\includegraphics<1>[width=1\linewidth]{../plots/volume_variety_AR0}
			\includegraphics<2>[width=1\linewidth]{../plots/volume_variety_AR1}
			\includegraphics<3>[width=1\linewidth]{../plots/volume_variety_bible_AR1}
			\includegraphics<4>[width=1\linewidth]{../plots/volume_variety_bible_AR2}
			\includegraphics<5>[width=1\linewidth]{../plots/volume_variety_bible_AR3}
			\includegraphics<6>[width=1\linewidth]{../plots/volume_variety_bible_AR4}
			\includegraphics<7>[width=1\linewidth]{../plots/volume_variety_bible_AR5}
			\includegraphics<8->[width=1\linewidth]{../plots/volume_variety_bible_AR6}
		\end{figure}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\only<1>{\framebox[1.1\width]{A matrix of documents x words } \par}
			\only<2>{\framebox[1.1\width]{AR1: 1,848 documents x 3,528 words } \par}
			\only<3>{\begin{framed}
					The Luther Bible: 1,189 documents (chapters) x 11,973 words
			\end{framed}}
			%\only<3>{\framebox[1.1\width]{The Luther Bible: \par 1,189 documents (chapters) x 11,973 words } \par}
			\only<4>{\framebox[1.1\width]{AR2: 6,941 documents x 15,781 words } \par}
			\only<5>{\framebox[1.1\width]{AR3: 18,728 documents x 27,730 words } \par}
			\only<6>{\framebox[1.1\width]{AR4: 44,000 documents x 45,388 words } \par}
			\only<7>{\framebox[1.1\width]{AR5: 108,277 documents x 75,553 words } \par}
			\only<8->{\framebox[1.1\width]{AR6: 128,357 documents x 86,149 words } \par}
		\end{center}
		\only<9->{		
			\begin{center}
				\begin{itemize}
					\item Comprehensive, credible and relevant assessments become
					more challenging as the literature grows \citep{Minx2017l}
				\end{itemize}
				\begin{remark}[]
					To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
				\end{remark}
			\end{center}
		}
	\end{column}
\end{columns}

@@

\only<3->{
\textbf{Steps}
\begin{enumerate}
\item<4-> Download documents from Web of Science (WoS)
\item<5-> Match documents to reference lists from IPCC reports
\item<6-> Topic model stemmed document abstracts
\end{enumerate}
}
\end{frame}

@@

\normalsize
\begin{itemize}
\item \citep{Haunschild2016}
\item 309,697 documents
\end{itemize}
\end{column}
\begin{column}{0.35\linewidth}
\textbf{Caveats}
\begin{itemize}
\item Not perfect query (Expressio Unius Est Exclusio Alterius )
\item WoS not all peer-reviewed literature
\item Missing grey literature
\item Missing relevant literature not directly about climate change
\end{itemize}
\end{column}
\end{columns}
\end{frame}

@@

For each Reference:
\begin{itemize}
\item Check for case-insensitive title matches
\item Calculate the Jaccard similarity score for two word shingles every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Bib

\begin{frame}{Bibliography}
\small
\bibliography{../Mendeley.bib}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Extra slides

\appendix
\backupbegin

@@

\backupend
